Revealing Folk Schemas of Musical Genre and Social Category Associations via Relational and Geometric Methods\thanks{Reserved for acknowledgments}

### 2025-06-20 manuscript.tex

\begin{figure}[ht!]
    \centering
    \includegraphics[trim={7cm 0cm 6cm 0cm},clip, width=0.9\textwidth]{Plots/main.png}
    \caption{Heatmap matrix of the proportion of respondents associating each one of fifteen social labels (columns) with one of twenty musical genre categories (rows).}
    \label{fig:main}
\end{figure}

@@

\subsection*{Individual Backbone Extraction}
Because each dual projection is likely to over-estimate the perceived similarities between genres and labels at the level of the individual, I use backbone extraction on each individual projection---more specifically, the disparity filter \citep{serrano2009extracting-084}---to isolate the most significant genre-to-genre and label-to-label associations for each individual \citep{neal2014backbone-b29}.

>>>>

\begin{figure}[ht!]
    \centering
    \includegraphics[trim={7cm 0cm 6cm 0cm},clip, width=0.6\textwidth]{Plots/main.png}
    \caption{Heatmap matrix of the proportion of respondents associating each one of fifteen social labels (columns) with one of twenty musical genre categories (rows).}
    \label{fig:main}
\end{figure}

@@

\subsection*{Individual Backbone Extraction}
Because each dual projection is likely to over-estimate the perceived similarities between genres and labels at the level of the individual, I use backbone extraction on each individual-level projection---more specifically, the Stochastic Degree Sequence Model (SDSM)---to isolate the most significant genre-to-genre and label-to-label associations for each person \citep{neal2014backbone-b29}.
